---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```




# Mid-America Regional Council's COVID-19 Data

This repository holds all the code [MARC](https://www.marc.org/) uses to keep their [COVID-19 Data Hub](https://marc2.org/covidhub/) up to date for the Kansas City Region. It exposes the entire process for downloading the most up-to-date datasets from our MARC Data API and transforming it to the forms needed to feed the [COVID-19 Data Hub](https://marc2.org/covidhub/).

## How to use this repository?

### If you just want to download the base datasets directly as a zipped set of csv files, [Click Here]()
These files are updated as part of our process for pushing updated data to our publication server so they should match the data in the MARC Data API.

### If you want access to the API directly, the GET URL's are as follows:

*  Case, Death, and Test Data: </br><https://gis2.marc2.org/MARCDataAPI/api/covidcasedeathtest>  
    *  This is the time series of the back-updated Case, Death, Test data that MARC uses
*  Newly Reported Case, Death, and Test Data: </br><https://gis2.marc2.org/MARCDataAPI/api/covidcasedeathtestnewlyreported>
    *  This is the time series of Newly Reported Case, Death, Test data that MARC uses to provide an estimate of how many Cases, Deaths, and Tests were reported in the last 24 hours similar to how the media reports these values. This data is not back-updated.
*  Hospital Data: </br><https://gis2.marc2.org/MARCDataAPI/api/covidhospital>
    *  This is the time series of the back-updated Hospital data that MARC uses
*  **Note** The LastUpdated columns are in UTC time if downloading directly from the API. The time conversion to 'America/Chicago'/'Central' is implemented when downloading from the R package with the function `downloadBaseData()`


### If you want to implement the API or the R package into your pipeline using R

#### Make sure dependencies are installed:

Programs to install:

* R (From CRAN; latest version at time of writing was 4.0.3)
* RStudio (Helpful R IDE)

Once these programs are installed. Open up RStudio and install the {remotes} package by running:  
```{r}
install.packages('remotes')
```


Then install the Covid19MARCData package with:
```{r}
remotes::install_github('MARC-KC/Covid19MARCData')
```
This will launch a process that may install a bunch of packages that the Covid19MARCData package is dependent upon. Once completed you should be able to load the new package with:
```{r}
library(Covid19MARCData)
```
This will attach the package to your environment and allow you to call the package functions. See the section [Using the R package Covid19MARCData](#using-the-r-package-covid19marcdata) for more information.


## Using the R package Covid19MARCData 

#### Download the data

This is similar to calling the API directly, except that it loads the resulting table into the R session and does the conversion of the LastUpdated columns from UTC to Central time.  
You can download all three datasets using the same function with a different `type` argument:
```{r}
#Case, Death, and Test Data
cdtData <- downloadBaseData(type = "CDT")

#Newly Reported Case, Death, and Test Data
cdtNRData <-  downloadBaseData(type = "CDT_NewlyReported")

#Hospital Data
hospData <-  downloadBaseData(type = "Hospital")
```


## Where does the data come from?
See COVID Data Hub FAQ
